Testing Theories of Expectation Formation using Probabilistic Forecasts

### 2019-06-24 paper/Draft.tex
SPF FE and  Efficiency Results Both Ind and Pop

\begin{eqnarray}
\begin{aligned}
\bar E_{t|t} (y_{t+h}) & = \rho^h [(1-PH) \underbrace{\bar E_{t-1}(y_{t+h})}_{\text{Average prior}} + P \underbrace{\bar s_{t}}_{\text{Average Signals}}] \\
& = (1-PH) \bar E_{t-1}(y_{t+h}) + P [\epsilon_t, 0]' \\
& = (1-PH) \bar E_{t-1}(y_{t+h}) + P \epsilon_t
\end{aligned}
\end{eqnarray}

@@

As to the uncertainty, as it does not depend on realized signals and the precision is the same aross all agents, average variance is equal to the variance of each individual.

\begin{eqnarray}
\begin{aligned}
\bar Var_t (y_{t+h}) = \bar \Sigma^y_t
\end{aligned}
\end{eqnarray}

@@

\begin{eqnarray}
\Delta Var_t(y_{t+h}) < 0 
\end{eqnarray}

>>>>

\begin{eqnarray}
\begin{aligned}
\bar y_{t+h|t} & = \rho^h [(1-PH) \underbrace{\bar  y_{t+h|t-1}}_{\text{Average prior}} + P \underbrace{\bar s_{t}}_{\text{Average Signals}}] \\
& = (1-PH) \bar y_{t+h|t-1}+ P [\epsilon_t, 0]' \\
& = (1-PH) \bar y_{t+h|t-1} + P \epsilon_t
\end{aligned}
\end{eqnarray}

@@

As to the uncertainty, as it does not depend on realized signals and the precision is the same aross all agents, average variance $\bar \Sigma_{t+h|t}$ is equal to the variance of each individual.

@@

\begin{eqnarray}
\bar \Sigma^2_{t+h|t} -  \bar \Sigma^2_{t+h|t-1}< 0 
\end{eqnarray}
